\documentclass[11pt,a4paper]{article}
\usepackage{linguex}
\usepackage{tipa}
\usepackage{apacite,pslatex}
\usepackage{titling}
\title {Genitive Construction and Dissimilation in Afaan Oromoo}
\author {Tolemariam Fufa}
\date{October 2022}
\begin{document}
	\newcommand\keywords[1]{%
		\begingroup
		\let\and\\
		\par
		\noindent\textbf{Keywords:}\\#1\par
		\endgroup
	}
	\maketitle
	\begin{abstract}
		 
		This paper attempts to describe Afaan Oromoo genitive construction.	This paper is divided into 6 sections. The first section is an introduction to Afaan Oromoo genitive construction. Section 2 is discusses possessive genitives of Afaan Oromoo; the concern of this section is alienable possessive (ALP) and inalienable possessive (IAP) of Afaan Oromoo. Section three discusses descriptive genitive of the language. Section 4 deals with problem areas of genitive of genitives of Afaan Oromoo. Section 5 proposes solutions for problems of genitive of genitives. Section six concludes the paper.
	\end{abstract}
	\keywords{genitive, possessive, descriptive, alienable, inalienable}
	\newpage
	
	\section{Introduction}
	\label{sec:org462cb4a}
	
	The genitive construction usually associated to owenership of something.  In Afaan Oromoo the genitive case is 
	
	
	
	The genitive construction usually associated to ownership of something; it is often described as possessive case. But, close investigation shows that genitive construction includes possession, source, origin and description among other things; that is to say all issues concerning genitive case are not explainable in terms of possession. Therefore, genitive construction is treated in different ways in literature; it is often typed into various categories including possessive, subjective, source, origin, objective, partitive and descriptive genitive \cite{ELTcon}. Some researchers categorize genitive construction into two main categories; namely, possessive and descriptive genitive; these two main categories are further subdivided into subcategories as alienable and inalienable possessions, metaphorical, generic descriptive genitives \cite{rosenbach2006descriptive,gebregziabher2012alienable}. 
	
	
	The discussion of subjective, objective, source, material and partitive genitive is also common. Subjective and objective genitives are used when a noun is derived from a verb and modified by another dependent noun. If the dependent noun (modifier noun of the main noun) expresses the main noun that is derived from the original verb, it is claimed to be a subjective genitive; but, if the dependent noun (genitive) expresses the object of the main verb, the genitive is said to be objective genitive. In subjective genitive an action or idea is set forth as proceeding from the noun in subject position \cite[68]{greenlee1950genitive}. The subjective genitive expresses about the nature of subject of a sentence. It does’t refer to possession. 
	
	
	In Afaan Oromoo subjective and objective genitives cannot be distinguished morphologically or syntactically; they are expressed in the same with construction. Thus, subjective and objective ginitives are distinguished semantically. Therefore, context is the main determining factor in this case. \\
	
	\ex. 
	\ag.
	nam-ni isa jaal-at-a\\
	man(people)-NOM him love-MID-3MSS\\
	'People loves him.'\\
	
	\ex. 
	\ag.
	inni nama jaal-at-a\\
	he.NOM man(people) love-MID-3MSS\\
	'He loves people.'\\
	
	\ex. 
	\ag.
	jaalala nama-a\\
	love man(people)-GEN\\
	'People's love or love of people.'\\
	
	As shown above \emph{jaalala} 'love' is derived from the verb \emph{jaalata} 'loves'. The dependent is \emph{nama} 'people' in this context. The dependent \emph{nama} express the subjective genitive on the bases of example (1) provided that people loves him. If we take into consideration example (2), \emph{jaalala namaa} 'people's love' is also subjective genitive as long as \emph{inni} 'he' dedicated to welfare of humanity. But if we are talking about general observation love of human being for human being, \emph{jaalala namaa} 'love of people' becomes objective genitive. 
	
	
	Moreover, a source can be expressed by a genitive case \cite[69]{greenlee1950genitive}. \\
	
	\ex.
	\ag.
	caama bona-a\\
	drought summar-GEN\\
	'summer drought'\\
	
	\ex.
	\ag.
	lolaa ganna-a\\
	flood winter-GEN\\
	'winter flood'\\
	
	In (4) \emph{bona} 'summer' is considered to be the source of drought; and in (5) \emph{ganna} 'Winter' happens to be the source of flood. In both cases genitive is marked by lengthening the final short vowels of the corresponding nouns, \emph{bona} and \emph{ganna} respectively. 
	
	In order to clarify source genitive, let us consider the following examples:
	\ex.
	\ag.
	buna Kafaa\\
	coffee Wallaggaa.GEN\\
	'Kafaa coffee'\\
	
	\ex.
	\ag.
	k'amadii Arsii\\
	wheat Arsii.GEN\\
	'Arsii Wheat'\\
	
	\ex.
	\ag.
	hoolaa Wolayitaa\\
	sheep Harar.GEN\\
	'Wolayita sheep'\\
	
	Examples given in (6-8) are source genitives. (6) expresses coffee is from \emph{Kafaa}; the sources of wheat and bull are also expressed in the same way, namely from \emph{Arsii} and \emph{Wolayitaa} respectively. Because the dependent nouns in (6-8) have long final vowels, the genitive is marked by null morpheme. 
	
	Materials of which a thing is made can be expressed by the genitive case \cite[69]{greenlee1950genitive}.
	\ex.
	\ag.
	siree sibiilaa\\
	bed iron.GEN\\
	'iron bed'\\
	
	\ex.
	\ag.
	foon hoolaa\\
	meat sheep.GEN\\
	'mutton'\\
	
	\ex.
	\ag.
	mana \textipa{\!d}agaa\\
	house stone.GEN\\
	'stone house'\\
	
	In (9), the material from which a bed is made, in (10) a type of meat and in (11), a material from which a house is built are expressed by genitive \emph{sibiilaa} 'iron', \emph{hoolaa} 'sheep' and \emph{\textipa{\!d}agaa} 'stone' respectively.
	
	Not only materials of which a thing is made but also a purpose a material for which it is planned my be expressed by genitive. In this case word order is the reverse of examples given in (9-11).
	
	\ex.
	\ag.
	siibiila siree\\
	iron bed.GEN\\
	'bed iron'\\
	
	\ex.
	\ag.
	foon hoolaa\\
	meat sheep.GEN\\
	'meat sheep'\\
	
	\ex.
	\ag.
	\textipa{\!d}agaa manaa\\
	stone house.GEN\\
	'house stone'\\
	
	As shown above word order of genitive phrases given in (12-14) are the reverse of examples given in (9-11) to show that purpose and material genitives are expressed not only morphologically but also syntactically.
	
	A whole thing from which only a part is to be focused may expressed by genitive construction known as the partitive genitive \cite[:69]{greenlee1950genitive}. Although most partitive 
	constructions refer to a quantity or amount, some are used to indicate quality or behavior.  
	\ex.
	\ag.
	halkan walakkaa\\
	night half.GEN\\
	'middle of the night'\\
	
	\ex.
	\ag.
	lit'a gannaa \\
	beginning winter.GEN\\
	'beginning of winter'\\
	
	\ex.
	\ag.
	baha gannaa\\
	end winter.GEN\\
	'end of winter'\\
	
	\ex.
	\ag.
	barii Dilbataa\\
	dawn Sunday.GEN\\
	'dawn of the Sunday'\\
	
	The above given examples indicate time. In (15), \emph{halkan walakkaa} 'middle of the night' indicates not only amount of time (which is roughly 6 hours) but also quality or behavior linked to middle of the night which is silent and fearsome. Similarly, (16-18) indicate amount of time as well as behaviors associated with \emph{lit'a gannaa} 'beginning of winter', \emph{baha gannaa} 'beginning of winter' and \emph{barii Dilbataa} 'dawn of the Sunday'. In the beginning of winter farmers prepare themselves for farming season. By contrast end of winter is associated with new year celebrations and time of happiness and joy. Dawn of the Sunday is also linked with time of rest, worship and socialization. 
		
	In Afaan Oromoo, genitive constructions marked in six ways:\\
	
	(1) A noun ending in long vowel marked by null morpheme. For example,  in \emph{mana Jiraataa} 'Jiraataa's house' the dependent (possessor) \emph{Jiraataa} has long final vowel; therefore, there is no overt genitive marking in such case. That is to say the possessor \emph{Jiraataa} doesn't show any morphological change to indicate genitive construction. \\
	
	(2) If a noun ends with a short vowel, we mark genitive case by lengthening the short vowel \cite[183]{gragg1976oromo,gobena2019verb}. For example, in \emph{mana namaa} 'a man's house', \emph{nama} 'man' has final short vowel in absolute form; the final short vowel becomes long in genitive construction. \\
	
	(3) If a noun ends in consonant, we mark the genitive construction by suffixation of \emph{-ii} \cite{gobena2019verb}. For example in \emph{wark'ii ilkaanii} 'golden teeth' the noun \emph{ilkaan} 'teeth' ends with \emph{n}, to which the genitive mark \emph{-ii} is suffixed. A noun that got its vowel long is interpreted as the possessor of a noun that precedes it. \\
	
	(4) The genitive can be made by placing the pronoun \emph{kan} 'whose' between the head and dependent (possessor) nouns; for example \emph{mana kan k'ottuu} 'a farmers's house' \cite[183]{gragg1976oromo}. In Meca dialect the pronoun \emph{kan} is used for both masculine and feminine genders. But in \emph{Harar, Borena and Tullama} dialects \emph{kan} shows masculine while \emph{tan} shows feminine gender. For example, \emph{mana tan ishee} 'her house'. \\
	
	(5) Genitves of genitives which are not final retain their absolute form \cite[104]{owens1985grammar}. \\
	
	(6) By applying dissimilation rule to genitive of genitives;
	
	\ex.
	\ag.
	mana nama-a \\
	house man-GEN\\
	'a man's house'\\
	
	\ex.
	\ag.
	mana nama Jimmaa \\
	house man Jima.GEN\\
	'Jima man's house'\\
	
	(20) is a genitive of (19). In (19), the dependent noun \emph{namaa} 'man' has final long vowel to mark genitive construction. In genitive of a genitive shown in (20), \emph{namaa} loses its final long vowel where another namely, \emph{Jimmaa} becomes the second dependent.
	
	(6) Genitive construction can also be indicated by possessive pronouns. For example,\\
	\\
	\ex.
	\ag.
	mana koo \\
	house my \\
	'my house'\\
	
	\ex.
	\ag.
	mana kee \\
	house your\\
	'your house (sing)'\\
	
	\ex.
	\ag.
	mana ishee \\
	house her\\
	'her house'\\
	
	\ex.
	\ag.
	mana isaa \\
	house his\\
	'his house'\\
	
	\ex.
	\ag.
	mana keenya \\
	house our\\
	'our house'\\
	
	\ex.
	\ag.
	mana keessan \\
	house your\\
	'your house (pl)'\\

	
	In this paper I categorize genitive construction into two types: possessive and descriptive genitives. Descriptive genitives are genitive constructions which are not possessives \cite{rosenbach2006descriptive}.
	
	\section{Possessive Genitives}
	
	Genitive construction often employed to express possession \cite[68]{greenlee1950genitive}.
	In Afaan Oromoo, possessive genitive can be expressed either morphologically or syntactically. 
	
	\ex.
	\ag.
	mana Tolasaa\\
	house Tolasa.GEN\\
	'Tolasa's house'
	
	\ex.
	\ag.
	Tolasaa-n mana qab-a\\
	Tolasa-NOM house has-3MSS\\
	'Tolasa has a house.'
	
	\ex.
	\ag.
	obboleessa Boontuu\\
	brother Bontu.GEN
	'Bontu's brother'\\
		
	\ex.
	\ag.
	Boontuu-n obboleessa qab-di\\
	Bontu-NOM brother has-3FSS\\
	'Bontu has brother.'
	
	
	As shown in the above examples possessive genitives in (27) and (29) are expressed morphologically while (28) and (30) are expressed syntactically using verb to have \emph{qaba/qabdi}. 
	
	Possessive genitive is categorized into two types: alienable (APG) and inalienable possessions (APG) \cite{gebregziabher2012alienable}.
	
	\subsection{Alienable Possessive Genitive (APG)}
	
	Alienable possessions refers to possessions which have not fixed semantic relationships between the 
	possessor and the possessed nouns \cite{gebregziabher2012alienable}. That is to say alienable possessions can freely change ownership. These include materials such as car, house, computer, book, etc.
	
	\ex.
	\ag.
	kitaaba barataa\\
	book student.GEN\\
	'student's book'
	
	\ex.
	\ag.
	konkolaataa barsiisaa\\
	car teacher.GEN\\
	'teacher's car'

	\ex.
	\ag.
	bilbila shamarree\\
	phone girl.GEN\\
	'girl's phone'
	
	
	These examples indicate morphological APG. APG can be expressed syntactically by employing the verb to have \emph{qab-}. 
	
		
	\ex.
	\ag.
	Barataa-n kitaaba qab-a\\
	student-NOM book has-3MSS\\
	'A student has a book.'
	
	\ex.
	\ag.
	Barsiisaa-n konkolaataa qab-a\\
	teacher-NOM car has-3MSS\\
	'A teacher has car.'
	
	\ex.
	\ag.
	shamarree-n bilbila qab-di\\
	girl-NOM phone has-3FSS\\
	'A girl has phone.'
	
	These are genitive constructions expressed syntactically by employing the verb to have \emph{qaba/qabdi}.
	
	Concerning definite morpheme,  APG is symmetrical with analytical (syntactic) APG. For example, the definite marker can get attached to the main noun in morphological APG. 
	
	\ex.
	\ag.
	kitaab-icha barataa\\
	book-DEF student.GEN\\
	'a student's book/lit. a student's the book'
	
	\ex.
	\ag.
	konkolaat-icha barsiisaa\\
	car-DEF teacher.GEN\\
	'a teacher's car/lit. a teacher's the car'
	
	\ex.
	\ag.
	bilbil-icha shamarree\\
	phoone-DEF girl.GEN\\
	'a girl's phone/lit. a girl's the phone'
	
	In the above examples all the head nouns are marked for definite; and, all are grammatically correct. 
	
	The dependent noun in the possessive genitive can also be marked for definiteness. 
	
	\ex.
	\ag.
	kitaaba barat-ichaa\\
	book-DEF student.GEN.DEF\\
	'the student's book'
	
	Both the head noun and the dependent nouns may also be marked for definiteness in Afaan Oromoo.
	
	\ex.
	\ag.
	bilbil-icha shamarr-ittii\\
	phoone-DEF girl.GEN.DEF\\
	'the girl's phone/lit. the girl's the phone'
	
	Similarly, analytic APG allows for the complement of the verb to have to be marked for definite. 
	
	\ex.
	\ag.
	barataa-n kitaab-icha k'ab-a\\
	student-NOM book-DEF has-3MSS\\
	'A student has the book.'
	
	\ex.
	\ag.
	barsiisaa-n konkolaat-icha k'ab-a\\
	teacher-NOM car-DEF has-3MSS\\
	'A teacher has the car.'
	
	\ex.
	\ag.
	shamarree-n bilbil-icha k'ab-di\\
	girl-NOM phone-DEF has-3FSS\\
	'A girl has the phone.'
	
	As shown above head nouns of genitive construction which are complements of the verb to have permits  for the definite morpheme \emph{-icha} to get attached to theme.
	
	
	The head noun of the APG can be a genitive construction. 
	
	\ex.
	\ag.
	kitaaba herreega-a barataa\\
	book maths-GEN student.GEN\\
	'student's maths book'\\

	\ex.
	\ag.
	barataan kitaaba herreegaa qab-a\\
	student book  maths.GEN has-3MSS\\
	'A student has maths book.'\\
	
	As shown above  in (43) and (44) the head noun is a genitive construction. In genitive structure such as shown in (43), \emph{kan} 'of' can be added. 
	
	\ex.
	\ag.
	kitaaba kan barataa\\
	book of student.GEN\\
	'student's book/book of a student'\\
	
	\ex.
	\ag.
	kitaaba herreega-a kan barataa\\
	book maths-GEN of student.GEN\\
	'student's maths book/maths book of a student'\\
	
	
	
	The word \emph{kan} is added after the head noun. In the analytic structure shown below the word \emph{kan} 'of' can be optionally added. In this case it is not 'student's book of maths' but 'book of maths' as shown below.
	
	\ex.
	\ag.
	barataan kitaaba kan herreegaa qab-a\\
	student book  of maths.GEN has-3MSS\\
	'A student has a book of maths.'\\
	
	If the head noun is modified by an adjective or a quantifier, the morphological ALP need the insertion of \emph{kan} 'of' to be grammatical while the analytic structure of ALP doesn't. 
	
	\ex.
	\ag.
	*kitaaba guddaa barataa\\
	book big student.GEN\\
	'student's big book'\\
	
	\ex.
	\ag.
	kitaaba guddaa kan barataa\\
	book big of student.GEN\\
	'student's big book'\\
	
	\ex.
	\ag.
	*kitaab-ilee lama barataa\\
	book-PL two student.GEN\\
	'student's two books'\\
	
	\ex.
	\ag.
	kitaab-ilee lama kan barataa\\
	book-PL two of student.GEN\\
	'student's two books'\\
	
	(47) and (49) are ungrammatical because the head nouns of the possessive genitives are modified by an adjective and a quantifier. But, (48) and (50) are grammatical because the head nouns of the genitives are modified and the word \emph{kan} 'of' is inserted preceding the dependent nouns. 
	
	By contrast, the analytic APG is grammatical if modified by an adjective or a quantifier without an addition of the word \emph{kan} 'of' as shown below.
	
	\ex.
	\ag.
	barataa-n kitaaba guddaa k'ab-a\\
	student-NOM book big has-3MSS\\
	'A student has a big book.'
	
	\ex.
	\ag.
	barataa-n kitaab-ilee lama k'ab-a\\
	student-NOM book-PL two has-3MSS\\
	'A student has two books.'
	
	As far as morphological ALP is concerned the more modifier stuff is added, the less the genitive construction becomes transparent and the less grammatical the structure would be. 
	
	\ex.
	\ag.
	*kitaaba herreega-a guddaa barataa\\
	book maths-GEN of big student.GEN\\
	'student's big maths book/big maths book of a student'\\
	
	\ex.
	\ag.
	kitaaba herreega-a guddaa kan barataa\\
	book maths-GEN of big of student.GEN\\
	'student's big maths book/big maths book of a student'\\
	
	\ex.
	\ag.
	*kitaaba herreega-a guddaa sana barataa\\
	book maths-GEN of big that student.GEN\\
	'student's that big maths book/that big maths book of a student'\\
	
	\ex.
	\ag.
	kitaaba herreega-a guddaa sana kan barataa\\
	book maths-GEN of big that of student.GEN\\
	'student's that big maths book/that big maths book of a student'\\
	
	As shown above (56) and (58) are less acceptable because in (56) an adjective \emph{guddaa} 'big' is added to the already heavy main noun \emph{kitaaba herreegaa} 'maths book' as a result of which the meaning of ALP becomes less transparent. The same case is true with (58) where an adjective \emph{guddaa} 'big' and a demonstrative \emph{san} 'that' are added. But if the word \emph{kan} 'of' is inserted preceding the dependent noun as shown in (57) and (59), both possessive genitives become acceptable. 
	
	As compared to morphological ALP analytic ones remain grammatically acceptable whether or not an adjective or a demonstrative added to modify the main noun of the genitive.
	
	\ex.
	\ag.
	barataa-n kitaaba herreegaa guddaa k'ab-a\\
	student-NOM book maths.GEN big has-3MSS\\
	'A student has a big maths book.'
	
	\ex.
	\ag.
	barataa-n kitaaba herreegaa guddaa sana k'ab-a\\
	student-NOM book maths.GEN big that has-3MSS\\
	'A student has that big maths book.'
	
	In the analytic ALP, the word \emph{kan} 'of' can be optionally inserted preceding the verb to have \emph{k'ab-} 'has'.
	
	\ex.
	\ag.
	barataa-n kitaaba kan herreegaa guddaa k'ab-a\\
	student-NOM book of maths.GEN big has-3MSS\\
	'A student has a big book of maths.'
	
	\ex.
	\ag.
	barataa-n kitaaba kan herreegaa guddaa sana k'ab-a\\
	student-NOM book of maths.GEN big that has-3MSS\\
	'A student has that big book of maths.'
	
	If the complement of the verb to have is not a genitive itself, the word \emph{kan} 'of' cannot be used in the analytic ALP.
	
	\ex.
	\ag.
	*barataa-n kitaaba kan guddaa k'ab-a\\
	student-NOM book of big has-3MSS\\
	'A student has a big book.'
	
	\ex.
	\ag.
	*barataa-n kitaaba kan guddaa sana k'ab-a\\
	student-NOM book of big that has-3MSS\\
	'A student has that big book.'
	
	
	\subsection{Inalienable Possessive Genitive (IPG)}
	
	Inalienable genitives (IPG) are possessive cases which forms a fixed semantic relationship between the possessor and the  possessee; kinship and body part possessive genitives are considered to be prototypes of IPG \cite[161]{gebregziabher2012alienable}. 
	
	\ex.
	\ag.
	abbaa gurbaa\\
	father boy.GEN\\
	'a boy's father'\\
	
	\ex.
	\ag.
	rifeensa hintala-a\\
	hair girl-GEN\\
	'a girl's hair'\\
	
	As shown in (66), the possessor or the dependent noun is \emph{gurbaa} 'boy' wile the possessee is \emph{abbaa} 'father'. In this the possessor and the possessee form fixed semantic relationship in the sense that the former is defined relative to the latter or vice versa. 
	
	Similarly, in (67) the noun \emph{rifeensa} 'hair' is defined in relation to the possessor which happens to be a specific individual. Body parts inherently require to be part of somebody \cite[161]{gebregziabher2012alienable}.
	
	In Afaan Oromoo IPG is expressed in the same as APG be it morphological or syntactic as shown below. \\
	
	APG
	
	\ex.
	\ag.
	mana hintala-a\\
	house girl-GEN\\
	'a girl's house'\\
	
	\ex.
	\ag.
	hintall-i mana k'ab-di\\
	girl-NOM house has-3FSS\\
	'A girl has house.'\\
	
	IPG
	
	\ex.
	\ag.
	rifeensa hintala-a\\
	hair girl-GEN\\
	'a girl's hair'\\
	
	\ex.
	\ag.
	hintall-i rifeensa k'ab-di\\
	girl-NOM hair has-3FSS\\
	'A girl has hair.'\\
	
	In Afaan Oromoo, the main noun of the IPG can be modified by another IPG.
	
	\ex.
	\ag.
	abbaa gurbaa\\
	father boy.GEN\\
	'a boy's father'\\
	
	\ex.
	\ag.
	abbaa abbaa gurbaa\\
	father father.GEN boy.GEN\\
	'a boy's father's father'\\
	
	\ex.
	\ag.
	abbaa eessuma/abeeraa gurbaa\\
	father uncle.GEN boy.GEN\\
	'a boy's uncle's father'\\
	
	\ex.
	\ag.
	abbaa abbaa eessuma/abeeraa gurbaa\\
	father father.GEN uncle.GEN boy.GEN\\
	'a boy's uncle's father's father'\\
	
	As shown in (73), the head noun of IPG is modified by another similar noun \emph{abbaa} 'father'. In (75), the head noun of the possessive genitive is modified by another possessive genitive, namely \emph{abbaa eessuma/abeeraa} 'uncle's father'. 
	
	The above extended IPG can be expressed syntactically as shown below.
	
	\ex.
	\ag.
	gurbaa-n abbaa k'ab-a\\
	boy-NOM father has-3MSS\\
	'A boy has father.'\\
	
	\ex.
	\ag.
	gurbaa-n abbaa abbaa k'ab-a\\
	boy-NOM father father.GEN has-3MSS\\
	'A boy has father's father.'\\
	
	\ex.
	\ag.
	gurbaa-n abbaa eessuma/abeeraa k'ab-a\\
	boy-NOM father uncle.GEN has-3MSS\\
	'A boy has uncle's father.'\\
	
	\ex.
	\ag.
	gurbaa-n abbaa abbaa eessuma/abeeraa k'ab-a\\
	boy-NOM father father.GEN uncle.GEN has-3MSS\\
	'A boy has uncle's father's father.'\\
	
	It is natural to modify the dependent noun (possessor) in IPG.
		
	\ex.
	\ag.
	abbaa gurb-icha-a\\
	father boy-DEF-GEN\\
	'the boy's father'\\
	
	\ex.
	\ag.
	rifeensa hintal-ittii\\
	hair girl-DEF.GEN\\
	'the girl's hair'\\
	
	In IPG, modifying the head noun by a determiner is less acceptable in Afaan Oromoo.
	
	\ex.
	\ag.
	*abb-icha gurbaa\\
	father-DEF boy.GEN\\
	'a boy's the father'\\
	
	\ex.
	\ag.
	*rifeens-icha hintala-a\\
	hair-DEF girl.GEN\\
	'a girl's the hair'\\
	
	\ex.
	\ag.
	*abb-icha gurb-icha-a\\
	father-DEF boy-DEF-GEN\\
	'the boy's the father'\\
	
	\ex.
	\ag.
	*rifeens-icha hintal-ittii\\
	hair-DEF girl-DEF.GEN\\
	'the girl's the hair'\\
	
	In (83) and (83) head nouns of the corresponding alienable possessives are modified by the definite marker \emph{-icha} 'the'. In both cases alienable possessives are less acceptable. In (84) and (85) both the head and dependent nouns are modified by definite markers \emph{-icha, ittii}; yet, the phrases fail to be alienable possessive construction. 
	
	In Afaan Oromoo, the possessor noun can be modified by an adjective and definite marker.
	
	\ex.
	\ag.
	obboleessa   gurbaa diim-aa\\
	brother 	boy red-M.GEN\\
	'a red boy's brother'\\
	
	\ex.
	\ag.
	harka hintala diim-tuu\\
	hand girl red-F.GEN\\
	'a red girl's hand'\\
	
	\ex.
	\ag.
	gurbaa diim-aa-n obboleessa k'ab-a\\
	boy    red-M-NOM brother has-3MSS\\
	'A red boy has brother.'\\
	
	\ex.
	\ag.
	*hintala diim-tuu-n harka k'ab-di\\
	girl red-F-NOM hand has-3FSS\
	'A red girl has hand.'\\
	
	\ex.
	\ag.
	hintala diim-tuu-n harka bareed-duu k'ab-di\\
	girl red-F-NOM hand beautiful-F has-3FSS\\
	'A red girl has a beautiful hand.'\\
	
	As shown in (86) and (87) dependent nouns are modified by adjectives. But as shown in (89) head noun of a body part cannot be expressed analytically unless modified by an adjective while kinship possessive genitives can be expressed analytically without being modified by adjective as shown in (88). 
	
	Moreover, the possessor in IPG can be modified by an adjective, definite marker and demonstrative pronouns.
	
	\ex.
	\ag.
	obboleessa   gurb-icha diim-aa\\
	brother 	boy-DEF red-M.GEN\\
	'the red boy's brother'\\
	
	\ex.
	\ag.
	obboleessa   gurb-icha diim-aa sana-a\\
	brother 	boy-DEF red-M that-GEN\\
	'that (the) red boy's brother'\\
	
	\ex.
	\ag.
	harka hintal-ittii diim-tuu\\
	hand girl-DEF red-F.GEN\\
	'the red girl's hand'\\
	
	\ex.
	\ag.
	harka hintal-ittii diim-tuu sana-a\\
	hand girl-DEF red-F that-GEN\\
	'that (the) red girl's hand'\\
	
	In (90) and (92) the dependent noun or the possessors are modified both by adjective and definite marker; and, in (91) and (93) the head nouns are modified by adjective, definite marker and demonstrative. 
	
	IPG can be expressed both analytically and morphologically. Therefore, analytic counterparts can be shown below.
	
	\ex.
	\ag.
	gurb-ich-i diim-aa-n obboleessa k'ab-a\\
	boy-DEF-NOM red-M-NOM brother has-3MSS\\
	'The red boy has brother'\\
	
	\ex.
	\ag.
	gurb-ich-i diim-aa-n sun obboleessa k'ab-a\\
	boy-DEF-NOM red-M-NOM that brother has-3MSS\\
	'That (the) red boy has brother'\\
	
	\ex.
	\ag.
	hintal-ittii diim-tuu-n harka bareed-duu k'ab-di\\
	girl-DEF.F red-F-NOM hand beauitful-F has-3FSS\\
	'The red girl has a beauitful  hand.'\\
	
		
	\ex.
	\ag.
	hintal-ittii diim-tuu-n sun  harka bareed-duu k'ab-di\\
	girl-DEF.F red-F-NOM that hand beautiful-F has-3FSS\\
	'That (the) red girl has a beautiful  hand.'\\
	
	
	
	
	\section{Descriptive Genitive}
	
	
	
	\begin{enumerate}
		\item how do descriptive genitives differ from possessive genitives?
		\item Are descriptive genitives syntactic, morphological or compounds?
		\item How do descriptive genitives differ from N + N sequences?
	\end{enumerate}
	
	Descriptive genitive is not an NP but usually a noun. Genitive constructions in which the possessor functions as a determiner have NP status and they denote a specific entity.Possessive genetives expands nominals into noun phrases. Semantically, possessive genitives specify (in)definiteness and establish reference within the NP \cite[82]{rosenbach2006descriptive}. In contrast the dependant in descriptive genitives is not an NP but usually a noun. The semantic difference between determiner genitives and descriptive genitives as discussed above are reflected in different positions in Afaan Oromoo noun phrases. Word order in the noun phrase is iconically determined in that any element contributing to the denotation of the head noun is positioned adjacent to the head, while anything contributing to the reference of the noun phrase will be most distantly located away from the head noun \cite[81]{rosenbach2006descriptive}.
	
	Therefore descriptive genitives are themeselves not full NPs but nouns or nominals and, in contrast to 	determine genitives, they denote properties and not specific entities. 	Semantically, the dependent in descriptive genitives contributes to the denotation of the head noun, not to the spacification of it. The dependant noun has a classifiying function in such genitives. As a classifier, the dependent is not referential and does not refer to a specific referent. 
	
	In Afaan Oromoo, the head noun cannot be determined by definite article. But, the head can be separately determined by definite article or by other reference tracking devices in possessive genitives.
	
	\ex.
	\ag.
	mana citaa \\
	house straw.GEN\\
	'a straw house'\\
	
	\ex.
	\ag.
	*mana-icha citaa \\
	house-DEF straw.GEN\\
	'the straw house'\\
	
	\ex.
	\ag.
	*mana cit-icha-a \\
	house straw-DEF-GEN\\
	'the straw house'\\
	
	\ex.
	\ag.
	*mana-icha cit-icha-a \\
	house-DEF straw-DEF-GEN\\
	'the straw house'\\
	
	(99) is a descriptive genitive where both the head and dependent nouns are not modified by definite article. (100), (101) and (102) are not acceptable because the head and dependent nouns are modified by definite article. By contrast the following examples of possessive genitive are acceptable.
	
	\ex.
	\ag.
	mana nama-a\\
	house mana-GEN\\
	'Someone's house/lit. a mana's house'\\
	

	\ex.
	\ag.
	mana nam-icha-a\\
	house mana-DEF-GEN\\
	'(the) someone's house/lit. (the) mana's house'\\
	
	Semantically, the possessor \emph{namaa} 'man's' in (103) functions like the definite article, specifying the referent of the NP. In this example \emph{namaa} specifiees whose house it is, namely someone's. From a cognitive-pragmatic and semantic point of view the possessor can be viewed as an 'anchor' that narrows down the referent of the NP \cite[80]{rosenbach2006descriptive}. In Afaan Oromoo, the dependent can be modified by definite article or demonstrative pronouns as discussed earlier in APG and IPG sections.
	
	In Afaan Oromoo the possessor can be postmodified and can be headed by a final determiner and demonstratives. But descriptive genitives cannot be modified by definite article but posmodified by demonstrative.
	
	\ex.
	\ag.
	mana citaa \\
	house straw.GEN\\
	'a straw house'\\
	
	\ex.
	\ag.
	mana citaa sana \\
	house straw.GEN that\\
	'that  straw house'\\
	
	\ex.
	\ag.
	mana nam-icha sana-a\\
	house mana-DEF that-GEN\\
	'that (the) someone's house/lit. that (the) mana's house'\\
	
	As shown in (106), the demonstrative \emph{sana} 'that' has short final vowel; it is not marked for genitive case; it is the dependent \emph{citaa} 'straw's' that is marked for genitive case to show that the dependent is not NP, but N. But the dependent in (107) is NP because the demonstrative \emph{sanaa} is marked for genitive case while the dependent \emph{citaa} 'straw' is not; this shows that the dependent in possessive genitive is an NP. 
	
		
	The interpretation of Afaan Oromoo genitive construction is clear if two nouns are involved; but, if more than two nouns are involved ambiguities arise. This means that if a genitive construction is 
	formed by three nouns, the second noun can be interpreted either as possessor (concerning the preceding noun) or as the possessed noun (concerning the
	following noun). A genitive construction that involves more than two nouns happens to be ambiguous and becomes source of public arguments.
	
	A descriptive genitive can be classifying, metaphorical, and generic one. It specifies another noun. 
	\begin{enumerate}
		\item Digrii Lammaffaa
		\item Gulantaa lammaffaa
		\item Itti aanaa Ministeeraa
	\end{enumerate}
	
	
	ARE DESCRIPTIVE GENITIVES SYNTACTIC PHRASES OR COMPOUNDS?
	
	(a) Coordination test
	
	Rosenbach, A. (2006: 83) gives three criterion to test if descriptive possessors are syntactic or cmpound. 
	First criterion is Coornation test. In Afaan Oromoo, coordination of dependant is common with descriptive genitives. 
	9a. foon hoolaa
	9b. foon reettii
	9c. foon hoolaafi reettii
	10a. mana dhagaa
	10b. mana mukaa
	10c. dhagaa manaa
	10d. dhagaafi muka manaa
	11a. reettii foonii
	11b. hoolaa foonii
	11c. reettiifi hoolaa foonii
	12a. hoolaa hormaataa
	12b. reetti hormaataa
	12c. reettiifi hoolaa hormaataa
	
	
	Because compounds do not allow a third element to be inserted between theme, these examples indicte taht descriptive genitives are syntactic phrases 
	and not compounds. 
	
	(b) Modification of the dependent
	
	If an N + N construction is a compound, then it should not be possible to separtely modify the first noun. 
	
	13a. foon hoolaa
	13b. foon hoolichaa
	
	
	In fact it should be noted that the dependent in descriptive genitives gives a different interpretation after modification.
	In hoolaa'sheep' is not a determiner, it expresses a type, not specifying foon 'meat'. 
	
	(c) Modification of the head
	
	As Rosenbach, A. (2006: 85) says, the strongest test for phrasehood is the ability of a modifier to intervene between
	the dependent and the head noun as shown below:
	14a. foon hoolaa
	14b. foonicha hoolaa
	15a. boojjitoo marqaa
	15b. boojjitoowwan marqaa
	
	As shown above -icha and -oowwan are added to the head by intervening between the dependent and the head noun
	to rule out compound status. 
	
	HOW DO DESCRIPTIVE GENITIVES DIFFER FROM N + N SEQUENCES? (p, 89) (there is no N + N) in Afaan Oromoo
	
	Descriptive genitives shown so far are known as classifying genitives. These genitives are said to be the prototypical cases 
	Rosenbach, A. (2006: 91). 
	
	\subsection{TYPES OF DESCRIPTIVE GENITIVES}
	
	Rosenbach, A. (2006: 92) argues there are three different functions of descriptive genitives: classifying, metaphorical and generic ones. 
	Classifying genitives are the ones usually referred to in the literature as 'descriptive genitives' (p, 92). These genitives
	are used to name certain objects and they can convey various degrees of lexicalization, from completely oqpaque expressions
	to fully semantically transparent ones (p, 92). 
	16a. ija bunaa
	16b. gumaa garbuu
	16c. arraba ibiddaa
	16d. guyyaa dubartootaa, Seera Makkoo Billii, 
	16e. harbuu Bantii
	16f. buqqee seexanaa (sheexanaa)
	(it includes, idiomatic expressions, plant names, insect names, named after person (p, 92). Product names, others
	\begin{verbatim}
		girl's school, writers block, spider's web ...etc (p, 93)
	\end{verbatim}
	
	
	In this naming function descriptive genitives are those that most clearly correspond to the term 'classifying genitives' as their basic
	function is type restriction. However, thhis only holds for semantically endocentric cases, where the dependent 
	clearly restricts the denotation of the head noun. In these cases the meaning of the head is the meaning of the 
	whole genitive NP, i.e. St Valentine's day designates a certain day, women's undrwea a certain type of underwear
	and smoker's cough a certain typeof cough, while a baby's head is not a type of head but a steak and kidney pudding.
	Similarly in (33d) the meaning of the whole genitive construction is not deducible compositionally from the meaning of the 
	head and the dependent attribute.. Rather, in these cases teh descriptive genitive refers to a complete mess (dog's breakfast) or to a specific type of balcony 
	(widow's walks). While they are not as such transparent, knowledge of the etymology of these idiomatic expressions makes them fully
	compositional in the figurative world, so to speak. For example, the term widow's walks (for porches on the roof)
	goes back to the fact (or rather legend?) that the wives of seafarers used to to climb up there to watch out for the 
	return of their husbands. Note, however, that even in the transparent cases (33e-g) the meaning of calassifying genives
	is much more restrictive than in a corresponding determiner genitive. Electrician's tape, for example, describes a specific
	type of tape, while a corresponding deterinmer genitive ([the elecrician's]tape) could mean various things: the 
	tape the electrician possesses, uses, wants to have, dreams of, or whatever. It is in the nature of possession to allow
	for all these meanings. As the function of the classifying genitives in (33) is to uniquely designate a specific object, it is 
	clear that not all these possessive  meanings carry over and taht , so to speak, one possessive meaning gets 'frozen' in these cases. 
	It is this 'freezing' of meaning which makes them so prone to undergo lexicalization and acquire lexeme  status. It is 
	presumably for this reason that Huddleston \& Pullum (2002: 470) regard this type fo genitive as 
	'a somewhat unproductive category'. They note, for example, taht while we can have a summer's day and a winter's day,
	a spring's day or an autumn's day are very questinable (they mark the latter two with a?). It is tru that the last two expressions are far less common than
	the first two. (p, 93). 
	
	Syntactic processes are by definition productive; it is usually only in the domain of word formation that the notion
	of productivity is evoked at all. As argued above descriptive genitives (in the sense of the calassifying genitive discussed here0
	can be syntactic phrases, and as such they should also be 'productive'. However, even when perceiving classifying genitives
	as being formed by the rules of word fromation, productivity is usually defined as the ability of a form to coin new
	expressions (p,94). That is, what matters is not how often a particular collection is used, but whether it is possible to coin
	it in the first place. In the examples above, it is the actual frequency of use that makes the difference. Thus, notice
	that both 'a spring's day and 'an autumn's day' can be used perfectly well to refer to a certain type of day; it is just
	that for seme reason they don't happen to be particularly frequent \ldots{} p, 94. While frequency of use may give us an indication
	as to the degree of lexicalization, it doesn't tell us anything about the productivity of the form/construction. 
	
	Note that, in general, new classifying genitives can be easily formed on the spot wheneve we perceive something as defining a type.
	Classifying genitives are fully productive (p, 94). 
	
	
	\subsubsection{Metaphorical genitives}
	
	Another type of descriptive genitives is used to describe an object, experience, state etc. in terms of another (p, 94). 
	one. 
	
	\begin{enumerate}
		\item akka dhala sooressaa (meeshaa mi'aawaa bituu jaalata)
		\item hamma baallee shimbirroo hin'ulfaatu
		\item 
	\end{enumerate}
	
	In (37a) the weight fo a swan's feather is used to describe the (light) weight of a person. In (37b) the well-known sound
	of a a dentist's drill characterizes the (ghastly) sound of a person's voice. The strength/intensity of the wind 
	is compared in (37c) to a prize fighter's blow. In (37d) the inner state of a person is described by means of the image
	of a child's inflatable toy. Note that in this last example the whole context is already in the metaphorical world:
	a word cannot lift a person literally. Rather, what is meant is that the word raises the person's spirits/mood, and 
	the way to get this image to the reader is to stay in this 'lifting' - metaphor and compare it with an inflatable toy
	(which can easily be lifted). The face in (37e) is compared to a child's pink ballon from which most of the air has escaped, 
	i.e. this image reinforces the description of the face as puffed and crumpled, and the colour of the ballon (pink)
	resembles the colour of the face. While in the examples in (37) the comparison is always made explicitly, most typically
	by expressions such as as, like , it reminded x of (p, 95). 
	
	
	In (38a) the person gives a yowl typical of cats. The person in (38b) does not of course literally have a puppy's 
	eyelashes, but eyelashes that look like those of a puppy. And in (38c) the child described is not a tennis umpire. 
	In fact, the whole setting is not a tennis setting, but it describes the settting of a play rehearsal by childeren,
	with the 'stage director' being physically located above her caste. That is, she does not literally have a tennis umpires's 
	advantage of height but only metaphorically -like a tennis umpire. (p, 95-96). 
	
	Note also that these metaphorical genitives can often be found in ellipitical constructions (p,96).
	
	In all these constructions the head of the genitive construction is omitted and refers back to a previously mentioned
	noun. This indicates taht such metaphorical genitives are phrases and not words. In many cases it is not clear whether the 
	initial article (usually the indefinet article) belongs to the dependent ofr to the whole genitive NP; however, examples (39a and c)
	show that (at least in these case) the singualr articcle goes with the (singular) dependent and not whth the (plural) head. 
	That is, structurally these genitives behave like determiner genitives. So, what -if anything - justifies their 
	classification as descriptive genitives?
	
	Note that in all the exampes avove the dependent is very clearly not specific. In fact, it cannot be, since the whole 
	possessive NP is not specific -as said, it serves as teh vehicle to transport a certain image into the (specific) context.
	Semantically, therefore, these construction are like descriptive genitives. They do not have the functin of a typical determiner, i.e. the referential
	anchoring of a referent, since the whole possessive NP as such is not specific. Rather, they evoke a certain typicl property 
	(hence, they are akin to what Strauss, 2004, calls 'propert-denoting possessives') (p, 96). 
	
	Under this view, we may regard these metaphorical uses of genitives as a type of determiner genitive operation in a 'subordinate mental space',
	facilitatin the identificaton of the referent of the (fictional) source domain. In this scenario we would first construe teh image
	of a fictioanl referent, i.e. a puppy, and then connect it to its eyelashes.. In this case we might argue that within this 
	fictional context, i.e. this subordinate mental space, a referent exists. That is, the dependent is specific in some irreal, 
	fictious world, but clearly unspecific in the  'real' world of discourse. Alternatively, however, we may also view them as a special case of 
	classifying genitive which is already akin to -but not identical with -determiner genitives. Under this view, then, 
	the unspecific dependent would not help to identify a (fictional) referent but a property. In this scenario, we construe
	eyelashes that are typical of puppies (in general), resulting in a nonsepecific interpretaion of the dependent. 
	Emperically, it is very difficult to decide which of the two conceptualization routes language users take (and see also
	section 4.1. on such constructional ambiguity). In any case, such metaphorical uses are very common. Not surprisngly, they are 
	most often found in fictional texts, such as novels, where metaphor is a common device to get across certain imaginative
	images or ideas. Metaphorical genitives are productive in the same way that determiner genitives ar, since they are modelled on them (p, 96-97)
	
	
	\subsubsection{Generic genitives}
	
	So far, we have only looked at the specificity of the dependent as a typical property distingushing determiner and 
	descriptive genitives. Under this view, the depedent in a descriptive genitive is unspecific in its naming function and 
	in tis comparing function, while it is specific in a determiner genitiv. However, specificity alone cannot account
	for all the referential properties genitive-marked dependents can have in English (Afaan Oromoo???). In this section I argue that it is important 
	to distinguis,, within the calass of nonspecific dependents, nonreferring dependents from referring (generic) dependents.
	
	Nonspecificity and genericity are often treated alike, but they are different notions with different properties. While specificity
	is a notion used to capture the referential properties of indefinite NPs, 'generic noun phrases are those in which 
	reference is made to an entire class' (C.Lyons, 1999:179). While specificity is a term usually only applied to indefinet
	NPs, generic NPs can also be expressed by definite NPs (The lion is a dangerous animal). Genericity is a concept that 
	can apply to both sentences and NPs. On the NP level, generic NPs have been considered as 'kind-referring' NPs by Krifka et al. (19995), 
	as opposed to 'object-referring' NPs, which denote a specific object/individual. A crucial difference between generic
	and nonspecific entities then is taht generics refer (to kinds), while nongeneric, nonspecific NPs don not refer at all.
	
	Now, how does all this relate to desriptive genitives? In (41) the dependent (a testator) is clearly not referring to 
	a specific testator. However, it does refer, as is evident from the susequent anaphor his which refers back to the 
	dependent(a testator). In contrast to determiner genitives this is not reference to a specific testator but referne to the 
	kind 'testaror', i.e. the dependent is 'kind-referring', i.e. generic.
	
	(41) Under family-provision legislation a testator's moral responsibility to provide for his dependents had become 
	a legal obligation in 1938 (p, 98).
	
	In contrast to metaphorical genitives, these genitives are not used to compare a referent in terms of another referent
	(or the referent's properties) but to describe a specific referent by setting it in relation to its kind. Note again
	that in the examples in (42) there is a specific refernt in the context that matches the generic possessor, a woman
	in (42a) 'a thin woman's apology', and a man in (42b) 'a man's horrible, humiliting sobbing'. In all these cases the 
	possessor abstracts away from the specific individuals, transcending them as examplars of a kind. Sometimes, this affinity
	of a specific referent in the context to its kind is even makde explicit, in a kind of mocking way, as in (43), or 
	or as describing the kind first and then finally identifying the matching (and co-present) referent, as in (44). 
	
	(43). So. What you're about, MrC.Shepherd. You here as the hopeful answer to a maiden's prayers? ..,
	(44) He was wanting a woman with a woman's way and a woman's knowledge, one who'd be as necessary to him as he was
	her. And you're that kind of woman, Val. \ldots{}(p, 98).
	
	There are other cases where the whole context is generic, and where therefore no potential specific referent is co-present
	and hence no ambiguity between the modes of speaking arises; example (45a) a woman's fear of breats cancer, (45b)
	a reader's respect, (45c) a woman's thought \ldots{} (p, 98).
	
	In all these examples the genitive NP receives a generic interpretation via the overall generic 'scripts' or 'frames'
	of the contexts \ldots{} That is, the overall context is generic and it is because of this overall generic setting that 
	the genitive therein is generic, too. However, withn this generic context the abstract refernts get individualized. 
	
	Note that we can also find generic dependents which are definite, while it was typical of the metaphorical genitives
	discussed in in secion 3.2. to have indefinete dependents. In fact, teh definite singual is often regarded as teh 
	prototypical generic expression \ldots{}
	
	In the examples in (46), 'the bad child's impulse to cry, the oversleepers's panicked sense of having fallen behind, 
	the optimistic Victorian's deep faith in progresss' \ldots{}the definite dependent is not specific but kind-referring;
	example (47) 'And he could do noting about his complexion, swarthier than the average Englishman's' illustrates that
	such generic definite dependents can also occur in ellipitic construction (p, 99). 
	
	Like metaphorical genitives, generic genitives behave structurally like determiner genitives, but semantically like
	descriptive genitives (with respect to their nonspecific dependent). Like metaphorical genitives, generic genitives are
	as productive as determiner genitives, as every individualized referent can be conceived of as a representaitve of its kind.
	(p,99). 
	
	
	As shown in the above examples (11) describes second degree, (12)  grade and (13) position. 
	
	\section{Problems Related to Genitive of Genitive in Afaan Oromoo}
	Biiroo
	Biiroo Misoomaa
	Biiroo Misooma Qabeenyaa
	Biiroo Misooma Qabeenya Bishaaniifi Inarjii Oromiyaa
	
	Biiroo Barnootaa
	Biiroo Barnoota Eegumsa Fayyaa
	Biiroo Barnootaa Eegumsa Fayyaa Oromiyaa
	
	The Flexibility of genitive in Afaan Oromoo
	Example                           Signaling
	koomee durba amuruu               'a physical attribute'
	obboleessa koo isa hangafa        'a blood relationship'
	abbaa manaa Uumee                'a non-blood relationship'
	alaqaa barreessituu              'a hierarchical relationship'
	hiriyaa barataa                  'a social relationship'
	garee Biiftuu                    'membership'
	beeksisa dhaabaa                 'performance'
	mana Jaalataa                    'ownership'
	gadda uummataa                   'emotional state'
	ergaa abbaashee                  'origin'
	kitaaba abbaashee isa jalqabaa   'human creation'
	dhimma biyyaa                   'topic'
	dhibee namichaa                'suffering/undergoing'
	meeshaa manaa                  'containing'
	huccuu bardheengaddaa          'the time of'
	foddaa gamoo                   'constituent part
	charjerii komputeraa           'associated part'
	madda odeeffannoo              'cause'
	miidhaa waraanaa               'result'
	
	
	The genitive determiner and pronoun system in Afaan Oromoo:
	
	Person, Gender, Number           Possessive Determiner             Possessive Pronoun
	1st person singular
	(all genders)                    koo (kitaabakoo)                       koo (kun kooti)
	
	1st person plural
	(all genders)                    keenya (kitaabakeenya)                keenya (kun keenyadha)
	
	2nd person singuar
	(all genders)                   kee (kitaaba kee)                     kee (kun  kitaabakeeti)
	
	2nd person plural
	(all genders)                  keessan (kitaaba keessan)              keessan (kun kitaaba keessanidha)
	
	3rd person singular
	masculine
	(all dialects                 isaa (ktaabasaa)                        isaa (kun kitaabasaati)
	
	3rd person singular
	feminine
	(all dialects)             ishee (kitaabashee)                       ishee (kun kitaabashee)
	
	3rd person plural
	all genders               isaanii (kitaabasaanii)                    isaanii (kun kitaabasaaniiti)
	
	3rd person singular
	neuter                    ---------                                 ----------------
	
	\section{Proposed Solution to Genitive of Genitive Problems in Afaan Oromoo}
	
	
	\section{Conclusion}
	
	\newpage
	\bibliographystyle{apacite}
	\bibliography{genitive}
	
	\newpage
	\section*{Acronyms and symbols}
	c=palatal,\\
	DEF=definite\\
	F=feminine
	lit.=literal\\
	M=masculine
	plosive, affricate\\
	GEN=genitive\\
	MID=middle\\
	pl=plural\\
	sing=singular\\
	
\end{document}
